A deeper look into bug fixes: patterns, replacements, deletions, and additions

### 2016-02-15 MSRChallenge2016.tex
reorg and a bunch of todos

\section{Introduction}
\todo{High level todo, probably for Mau since I think it's his bibtex: please
  change the bibtex keys to take the form ``lastnameYear'', and then fix the
  citations.}
\todo{Also, please always include a non-breaking space (a tilde, look at the
  latex for an example) between a word and the cite tag, and include multiple
  references on a line in a single citation tag (again, look at the latex for an
  example; I'll do this once, but would like you to fix the rest when appropriate.}
Automatic bug repair is the branch of computer science that deals with automated
ways to repair errors in software. There have been several approaches taken
towards improving the different methodologies to repair bugs in software
automatically \cite{dongsun,weimer,claire,kai}, one of the
most accepted approaches so far has been GenProg \cite{weimer}\cite{claire}, an
evolutionary program repair tool which applies four different kinds of possible
edits to code in order to find a patch for a given bug. These changes are the
following: Delete, Replace, Swap and Append.

@@

\subsection{Detecting PAR Bug Fixing Pattern}\label{sec:method}
The bug fixing patterns that we analyze in this work are adopted from Kim et al. paper~\cite{dongsun}. The following is the description of each considered pattern.
\begin{enumerate}
	\item {\bf Altering method parameters (AMP)}\\
	{\bf Example:} obj.method(v1,v2) $\rightarrow$ obj.method(v1,v3)\\
	{\bf Description:} This pattern changes the input for method parameters.
	\item {\bf Calling another method with the same parameters (MSM)}\\
	{\bf Example:} obj.method1(param) $\rightarrow$ obj.method2(param)\\
	{\bf Description:} This pattern changes the method name.
	\item {\bf Calling another overloaded method with one more parameter (COM)}\\
	{\bf Example:} obj.method(v1) $\rightarrow$ obj.method(v1,v2)\\
	{\bf Description:} This pattern adds one more parameter to the method.
	\item {\bf Changing a branch condition (CBC)}\\
	{\bf Example:} if(a != b) $\rightarrow$ if(a != b \&\& c == 0)\\
	{\bf Description:} This pattern adds or removes condition.
	\item {\bf Initializing an object (IAO)}\\
	{\bf Example:} Type obj $\rightarrow$ Type obj = new Type()\\
	{\bf Description:} This pattern adds a initialization to object declaration.
	\item {\bf Adding a null checker (ANC)}\\
	{\bf Example:} obj.m1() $\rightarrow$ if(obj!=null){obj.m1()}\\
	{\bf Description:} This pattern inserts a condition to check whether an object is null or not in order to prevent unexpected state.
	\item {\bf Adding an array out of bound checker (AOB)}\\
	{\bf Example:} arr[idx]=0 $\rightarrow$ if(idx<arr.length){arr[idx]=0}\\
	{\bf Description:} This pattern inserts a condition to check that an array index is within bound right before the index is used.
\end{enumerate}

@@

\end{enumerate}

@@

\section{Conclusions}
The findings of our study provide a set of useful guidelines for automatic program repair tools with which their search for a patch can be now improved by having the knowledge of how likely it is to replace a faulty statement by the different kinds of statements available.

@@

@@

>>>>

\section{Introduction}
\todo{High level todo, probably for Mau since I think it's his bibtex: please
  change the bibtex keys to take the form ``lastnameYear'', and then fix the
  citations.}
\todo{Please move the bibitems included explicitly in this document into sigproc.bib
   and use bibtex.}
\todo{Also, please always include a non-breaking space (a tilde, look at the
  latex for an example) between a word and the cite tag, and include multiple
  references on a line in a single citation tag (again, look at the latex for an
  example; I'll do this once, but would like you to fix the rest when appropriate.}
Automatic bug repair is the branch of computer science that deals with automated
ways to repair errors in software. There have been several approaches taken
towards improving the different methodologies to repair bugs in software
automatically \cite{dongsun,weimer,claire,kai}, one of the
most accepted approaches so far has been GenProg \cite{weimer}\cite{claire}, an
evolutionary program repair tool which applies four different kinds of possible
edits to code in order to find a patch for a given bug. These changes are the
following: Delete, Replace, Swap and Append.

\todo{We need to integrate the PAR and operator discussion a bit better.  Let's
  take it up a level of abstraction: there is initial work in applying these
  techniques to Java that propose a number of mutation operators, and we study
  the degree to which they apply in practice and make recommendations based on
  human-provided repairs.  Doing so is a good idea, because patches inspired by
  human-created repairs are empirically demonstrated to be rated more highly by
  developers (cite PAR).}
\todo{I also thought we were doing Par first, and then the replacement studies?}

@@

\subsection{Detecting PAR Bug Fixing Pattern}\label{sec:method}
The bug fixing patterns that we analyze in this work are adopted from Kim et
al. paper~\cite{dongsun}. The following is the description of each considered
pattern. 
\todo{Ferdian: why are we only studying 7?  It's OK to not study all of them,
  but we need to explain why.}
  \begin{enumerate}
	\item {\bf Altering method parameters (AMP)}\\
	{\bf Example:} obj.method(v1,v2) $\rightarrow$ obj.method(v1,v3)\\
	{\bf Description:} This pattern changes the input for method parameters.
	\item {\bf Calling another method with the same parameters (MSM)}\\
	{\bf Example:} obj.method1(param) $\rightarrow$ obj.method2(param)\\
	{\bf Description:} This pattern changes the method name.
	\item {\bf Calling another overloaded method with one more parameter (COM)}\\
	{\bf Example:} obj.method(v1) $\rightarrow$ obj.method(v1,v2)\\
	{\bf Description:} This pattern adds one more parameter to the method.
	\item {\bf Changing a branch condition (CBC)}\\
	{\bf Example:} if(a != b) $\rightarrow$ if(a != b \&\& c == 0)\\
	{\bf Description:} This pattern adds or removes condition.
	\item {\bf Initializing an object (IAO)}\\
	{\bf Example:} Type obj $\rightarrow$ Type obj = new Type()\\
	{\bf Description:} This pattern adds a initialization to object declaration.
	\item {\bf Adding a null checker (ANC)}\\
	{\bf Example:} obj.m1() $\rightarrow$ if(obj!=null){obj.m1()}\\
	{\bf Description:} This pattern inserts a condition to check whether an object is null or not in order to prevent unexpected state.
	\item {\bf Adding an array out of bound checker (AOB)}\\
	{\bf Example:} arr[idx]=0 $\rightarrow$ if(idx<arr.length){arr[idx]=0}\\
	{\bf Description:} This pattern inserts a condition to check that an array index is within bound right before the index is used.
\end{enumerate}

@@

\end{enumerate}
\todo{IMPORTANT: Ferdian, where did the results go?  Please add the results of
  the Par study into results somewhere where it fits.}

@@

@@

\todo{What is the dataset?}

@@

\todo{Is there room/call to include any element of Chu Pan's replacement
  analysis in here?}

\section{Conclusions}
The findings of our study provide a set of useful guidelines for automatic
program repair tools with which their search for a patch can be now improved by
having the knowledge of how likely it is to replace a faulty statement by the
different kinds of statements available.
\todo{Expand to include summary of actual conclusions}
